---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Install the package
```{r eval=FALSE}
# devtools::install_github("dhia-gharsallaoui/watervalues")

```
## Load the package
```{r Load the package, eval=TRUE}
# library(watervalues)

```


Now we are ready to use our package.

## Set the study
Use the package antaresRead to select the study in Input mode.
```{r warning=FALSE}
# library(antaresRead)
# study_path <- "D:/Users/gharsallaouidhi/Documents/20200722_MAF2025_S4_V2_7.1"
# opts <- antaresRead::setSimulationPath(path = study_path, simulation = "input")
```

## Start simulation
To generate the Reward Matrix of transitions, it's necessary to run a certain number of 
simulations *nb_disc_stock*. The larger this number is, the more precise rewards we get.

These simulations are launched from R with the `runWaterValuesSimulation()` function and are run by the Antares solver.
*NB:* A large number will cause a long time of simulation.

Skip this step if you already do it before and you have the Rdata file.

```{r eval=FALSE}
# simulation_res <- runWaterValuesSimulation(
#   area = "2_nom1_hydro_open",                        # name of area
#   simulation_name = "nom_def0_weekly_water_amount_%s",
#   path_solver="D:/Users/gharsallaouidhi/Documents/antares/rte-antares-8.0.3-installer-64bits/bin/antares-8.0-solver.exe",                 # solver path 
#   fictive_area = "watervalues_fr",    # name of the Fictive created area 
#   nb_disc_stock = n,                  # number of simulations
#   overwrite = TRUE,
#   nb_mcyears=15
# )
# save(simulation_res,"simulation_res.Rdata")
```
Save the output file in Rdata file to avoid losing the simulation information for the future calculation.

 * `area` is the relevant area.
 * `nb_mcyears` is the number of Monte-carlo year that will be generated. Here we
 limit it to 10 to increase speed.
 * `path_solver` is the path to the Antares solver.
 * `nb_disc_stock` is the number of values used to discretize the stock level between
 0 and the maximum value for the given area. Here 10 simulations are run, with 10
 binding constraints ranging from 0 to the maximum of hydro
 energy that can be produced over a week.
 * `overwrite` allows to overwrite the area, cluster and binding constraint if they
 already exist.
 
## Watervalues
```{r include=FALSE}
# load("~/R coding/sim_results_files/2_nom1 10 sim 10MC with BC.Rdata")
# simulation_res <- simulation_res2
```

Water values are generated in R with the `Grid_Matrx()` function, using the results
of the above simulations.
```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# 
# results <- Grid_Matrix(      area = "2_nom1_hydro_open",
#                              simulation_names = simulation_res$simulation_names,
#                              simulation_values = simulation_res$simulation_values,
#                              nb_cycle = 2,
#                              opts = opts,
#                              week_53 = 0,
#                              district_name = "water values district",
#                              method="mean-grid",
#                              states_step_ratio=0.025,
#                              max_mcyears=10,
#                              reservoir_capacity=NULL,
#                              correct_outliers = T,
# )


```
 
 
 * `area` is the relevant area.
 * `simulation_names` are the names of the simulations .
 * `simulation_values` are their values.
 * `week_53` are the water values for the last week of the year.
 * `nb_cycle` is the number of times to run the algorithm in a loop from the last
 week of the year to the first, in order to obtain more realistic start values for 
 week 53.
 * `method` is the algorithm to be used to calculate Bellman values. We have three algorithms for the moment
 tap `help(Grid_Matrix)` to learn about them.
The result is a 7-column `data.table`: Bellman values are in the `value_node` column,
and water values in the `vu` column.



