---
title: "User guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{user_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The `antaresWaterValues` package aims at generating and exporting water values for
Antares v7. In this vignette, we detail how to use it step by step.


## Setup

First we have to load `antaresWaterValues` and two helper packages. We also setup
the paths to the Antares study and to the solver:

```{r eval=FALSE}
library(antaresWaterValues)
library(antaresRead)
library(antaresEditObject)

# simulation path
antaresRead::setSimulationPath(path = "inputs/my_study/", simulation = "input")

# solver path
setSolverPath(path = "D:/Program Files/RTE/Antares/7.0.0/bin/antares-7.0-solver.exe")
```


## Simulations

Next, it's necessary to run a number of simulations in Antares. These simulations
are launched from R with the `runWaterValuesSimulation()` function and are run by
the Antares solver.





